\documentclass[12pt]{article}
\usepackage{url}
\usepackage[small,compact]{titlesec}
\usepackage[bookmarksopen,colorlinks,plainpages=false,urlcolor=blue]{hyperref}
\usepackage[czech]{babel}
\usepackage[utf8]{inputenc}
\usepackage{a4wide}
\usepackage[USenglish]{datetime}
\usepackage[pdftex]{graphicx}
%\renewcommand{\dateseparator}{.}


\begin{document}
\title{MI-PIS}


\dmyyyydate


\author{
\begin{tabular}{ l r } 
  \bf Author: Jiří Křížek & (\url{krizeji1@fel.cvut.cz})
\end{tabular}}

\maketitle
%\newpage

%\tableofcontents
%\newpage

\section{Project team}
  \subsection{Project code}
  Project code is "\texttt{FITPIS121P.L1800HKOPR}"
  
  \subsection{Project mail account}
  Project mail account is \url{fitpis121p.l1800hkopr@gmail.com}.
  
  \subsection{Team members}
    \begin{itemize}
      \item{{\bf Director:} Jiří Křížek (\url{krizeji1@fit.cvut.cz})}
      \item{{\bf Office manager:} Michal Pohořelý (\url{pohormic@fit.cvut.cz})}
      \item{{\bf Solution architect:} Martin Ovesný (\url{fitpis121s.355987@gmail.com})}
      \item{{\bf Solution architect:} Daniel Heglas (\url{hegladan@fit.cvut.cz})}
      \item{{\bf Finance manager:} Michael Rejzek (\url{rejzemic@fit.cvut.cz})}
    \end{itemize}

\subsection{Time schedule}

\begin{tabular}{|l|r|l|r|}
\hline
\bf{Report name} & \bf{Due date} & \bf{Responsible} & \bf{Sem. week} \\
\hline
\hline
{\bf Project team                } & 29 February 2012 & Jiří Křížek & week 3 \\
{\bf Project scope               } & 14 March 2012 & Jiří Křížek & week 5 \\
{\bf Detailed project schedule } & 21 March 2012 & Michal Pohořelý & week 6 \\
{\bf Func. decomposition } & 4 April 2012 & Martin Ovesný & week 8 \\
{\bf Solution architecture } & 4 April 2012 & Daniel Heglas & week 8 \\
{\bf Project budget } & 18 April 2012 & Michael Rejzek & week 10 \\
{\bf Final report - presentation } & 25 April 2012 & Michal Pohořelý & week 11 \\
{\bf Final report - document     } & 2 May 2012 & Michal Pohořelý & week 12 \\
\hline
\end{tabular}
\newpage
\section{Project scope - business proposal}
Author: Jiří Křížek
\subsection{Purpose of the plan, project scope}
The system will be used by employees and students of secondary schools or gymnasiums.
\subsection{Description of the project}
The project goal is to create a web application for evidence of employees, students and applicants. It will provide preparation of timetables or one-time reservation of the rooms. Teachers will be able to publish grades to students and each student will be able to see his grades. Web application will allow to create and publish overview of the school year.
\subsection{Project scope, goals}

\subsubsection{Scope}
Investments will not exceed 300 000Kč, total cost of ownership in 5 years will not exceed 600 000Kč.
\subsubsection{Main functionality}
The implemented system will be used for the needs of secondary schools or gymnasiums. 
\\
System will allow:
\begin{itemize}
\item{Assistance in the organization of entrance examinations}
\item{Keep records of applicants, students and employees}
\item{The evidence of study results (grades)}
\item{The timetables evidence, reservation of the rooms (one-time or periodically)}
\item{Events calendar, overview of the school year}
\end{itemize}

\subsubsection{Implementation}
According to size of the customer it is encouraged to use existing open source projects and adjust them to the needs of the school, eventually provide integration with other systems, if possible.
\subsubsection{Technical limitatations}
\begin{itemize}
\item{System will be available as a web application. }
\item{Programming language is Java.}
\end{itemize}
\end{document}
